Exploratory CNV analysis using inferCNV

### 2024-11-05 analyses/cell-type-wilms-tumor-14/exploratory_analysis/03_cnv/03_infercnv_SCPCL000850.Rmd

## Input files
# load pre-processed sample objs & anchor transfer results
obj <- SeuratObject::LoadSeuratRds( file.path(path_anal,"scratch","00_preprocessing_rds",paste0(library_id,".rdsSeurat")) )
level <- "compartment"
predictions <- read.csv( file.path(path_anal, "results", "01_anchor_transfer_seurat", paste0(library_id, "_", level,".csv")) ) 
obj <- AddMetaData(object = obj, metadata = predictions)
infercnv_result <- readr::read_rds( file = file.path(library_out_dir, "run.final.infercnv_obj") )
# add infercnv output to seurat object
obj_cnv <- infercnv::add_to_seurat(
  seurat_obj = obj,
  infercnv_output_path = library_out_dir
)
```

>>>>

## Input files
# load pre-processed sample objs & anchor transfer results
obj <- SeuratObject::LoadSeuratRds( file.path(path_anal,"scratch","00_preprocessing_rds",paste0(library_id,".rdsSeurat")) )
level <- "compartment"
predictions <- read.csv( file.path(path_anal, "results", "01_anchor_transfer_seurat", "RNA", paste0(library_id, "_", level,".csv")) ) 
obj <- AddMetaData(object = obj, metadata = predictions)
infercnv_result <- readr::read_rds( file = file.path(library_out_dir, "run.final.infercnv_obj") )
# add infercnv output to seurat object
obj_cnv <- infercnv::add_to_seurat(
  seurat_obj = obj,
  infercnv_output_path = library_out_dir
)
```
